%
% file: localoperator.tex
% author: Victor Brena
% description: Briefly describes properties of the local operator.
%

\chapter{Appendix A}
\label{app:app01}

(Brainstorming notes - project briefing) 

GitHub: \href{https://github.com/TeeThanakit/mariana-hotel}{https://github.com/TeeThanakit/mariana-hotel}

\textbf{Project name:} Hotel Management System

\textbf{Potential features:} Hotel Management, Reservation, Check-in/Checkout, Charges and Invoicing, House Cleaning, Room Rate Code, Seasons, Setup\\

\textbf{OUR SOFTWARE STACKS}

\begin{description}
	\item[Data Layer] Postgres (database) (use diesel, sqlx, or SeaORM), Redis or MongoDB for dev. period
	\item[Logic Layer:] Actix-web on Rust (production), Node.JS on Express (development version)
	\item[Presentation Layer:] Tailwind CSS (add some custom components that work with SvelteKit), Svelte (with Typescript and SvelteKit) for interactivity
\end{description}

This is just initial one.\\

\textbf{DEVELOPMENT INSTRUCTIONS}

\begin{enumerate}
	\item Choose a topic (already selected above).
	\item Clearly define the detail and scope of the project.
	\item Define major user views (user roles) and user permission levels (Note that your project must have at least three separate roles for users).
	\item Design your database and represent the design with an ER diagram with primary key, foreign key, and multiplicity. (Note that your project must have at least 7 tables so that each person in your group must have at least 1 complex transaction form with modification in 2 or more tables) and 1 advanced analytic report to (using at least three tables with aggregation functions) in the final project).
		\subitem Example of complex transaction form: The form must be able to modify at least 3 tables with one action (one click).
		\subitem Example of Analysis Report: The report must use at least one aggregate function. (e.g., Count, Sum, Avg., Min., and Max) and be used for decision making.
	\item Select appropriate data types for each attribute and generate a data dictionary (showing field names, constraints, and data types) for your database
	\item Develop a web/mobile application to connect with the designed database. (Note that each person in your group must have at least 1 complex transaction form (with modification in 2 or more tables) and 1 advanced analytic report to (using at least three tables with aggregate functions) in the final project).
\end{enumerate}

TBD for later changes on plans.\\

\textbf{GRADING CRITERIA:} 

This is the criteria for the final project grading: 

\begin{enumerate}
	\item Database design (30\%): The ER model or database model must be designed correctly for the topic selected. 
	\item Report (20\%): The detail and scope of the project, user permission level (Insert, Delete, Update, View) with each table for each user role, and data dictionary must be presented clearly and correctly.
	\item Web or Mobile Application (30\%): The form and analysis report represented in the developed application must be performed completely and correctly. 
	\item Presentation (20\%): Make your presentation interesting, clear to the point, within a time limit (10 minutes), and correct language usage.
\end{enumerate}

\