\chapter{Background}

\section[Domain Analysis]{Domain Analysis for the project}

With the intensified competition in hotel industry, their strive to improve their operational management has led to extensive use of "online hotel management system". These systems are dedicated to addressing hotel management issues in a more practical, well-organized, quick way of processing the service from hotel both nearby and remote customers with a more friendly GUI oriented experience. \cite{IJOE_Hotel_Management}

\subsection{Stakeholders and their concerns}

We distinguish primary and secondary stakeholders connected to this hotel organization. This helps us understand the domain of hotel better and do not mix features from other domain such as enterprise management. This process will follow to draw out entities, their attributes and relationships.

\subsubsection{Primary stakeholders}

We are especially going to deal with these stakeholders for the context of our application.

\begin{description}
	\item[Admin] They are the apex decision makers in the organization. They can be hotel owner, highest level of management or the IT staff being outsourced by the highest decision making authority.
	\item[Management] Staffs working on reception, dining, and other management related areas.
	\item[Ground staff] Staffs working on gardening, housekeeping, security. Management and ground staffs are supposed to have different level of abstraction when it comes to data access.
	\item[Guest] The end customer. They can be at the hotel for just dining, book room or attend conference. In such case guest entity can be a person or an organization that can book hotel facility for social gathering such as corporate parties, academic conferences, hackathons and much more.
\end{description}

\subsubsection{Secondary stakeholders}

Although they have some influential stake at the hotel industry, we are going to cut their concerns off as our product would be more close to ERP (Enterprise Resource Planning) tools by addressing their feature requests rather than hotel management application.

\begin{description}
	\item[Legal team] They oversee legal matters in the organization.
	\item[Audit team] Also known as auditors or charter accountant, they look after balance sheets, taxation and other fiscal affairs.
	\item[Human resources] They manage staff operations such as recruiting, training, performance assessment and so on.
	\item[Supply chain] This includes supply chain operations related to interior design, kitchen ingredients, gifts, and decoration being brought by business in a routine basis.
	\item[Procurement] This is part of occasional purchases rather than regular supply chain issue. This can cover damage control for accidents, damages to property \& their necessary replacement or even upgrade of hotel infrastructure.
\end{description}

\section[Existing Solutions]{Existing Solutions in the market}

Some of the prominent hotel operating system  (or more popularly known as property management system) include the following as of 2024: \cite{best_hotels_2024}

\begin{description}
	\item[Oracle Hospitality OPERA Cloud Services] They are a cloud-based, mobile-enabled platform for next-generation hotel management. Based on OPERA, the leading enterprise solution suite for the hospitality industry, OPERA Cloud offers an intuitive user interface, comprehensive functionality for all areas of hotel management, secure data storage and hundreds of key partner interfaces to meet the needs of hotels of all types and sizes. Oracle Hospitality is a proud AHLA Platinum Partner.
	\item[SkyTouch Technology] This company has provided the most widely-used hotel PMS software to solve all property management needs since 2013. Hoteliers seek our cloud-based software with 24/7 support for our easy-to-use interface abilities. Our products efficiently manage rates \& availability, distribution \& booking, guest experience, and more.
	\item[Cloudbeds] It is a leading platform serving thousands of properties in more than 150 countries worldwide.
	\item[RoomRacoon] It is an innovate all-in-one Hotel Management System for independent hotels, B7Bs, hotels, apartments, and vacation rentals. RoomRaccoon is one of the most connected solutions on the market and offers over 400 integration with business solutions such as Lightspeed, Sage, Booking.com and Expedia. 
	\item[WebRezPro] WebRezPro is a secure, one-stop-shop cloud property management system that streamlines operations for independent lodgings of all shapes and sizes. The automated, easy-to-use system saves time and money while boosting direct bookings and improving guest experience. 
\end{description}

Beside academic version, hotel management systems are also popular choice among IT and engineering institutes to give hands-on experience to student regarding the software engineering concepts like object-oriented software engineering and database management. \cite{IJOE_Hotel_Management}\cite{sri_lanka_HMS_2022}

\clearpage
%=========================================================