\chapter{Findings and Conclusion}

\section{Evaluation of Outcomes}

We have split our outcome evaluation to access both technical requirements of this database project and then learning outcomes of the CPE241 course.

\subsection{Technical Outcomes}

\begin{description}
	\item[Database Design] This is tested from E2E testing in order to find if the database design is actually functional and perform the desired functionally completely. Later, we normalized the relational structure followed by another end to end testing.
	\item[Adequate permission levels] Proper RBAC metadata is created and imported prior to any data operations via our software applications.
	\item[Forms and Reports] We have created transaction forms such that at least 3 tables are modified on one action. However, simple actions also exists within the application. Aggregate functions were used for calculating average bookings per month and net profit.
	\item[Application development] A complete three tier web application is developed to work hand in hand with the designed database. The unit testing was done thoroughly to check if the desired functions are handled properly.
\end{description}

\subsection[Learning Outcomes]{Learning Outcomes: Self Assessment}

Here is the summary to the very least:

\begin{enumerate}
	\item ER model was designed and improved progressively over time as our team's domain knowledge improved. It is prepared to best of our abilities and knowledge.
	\item Data dictionary and user permission level is included in the report.
	\item We developed a functional web application to interact with the database.
\end{enumerate}

\section{Conclusion}

We have explored and a hotel management system applying the best known software development practices using modern database concept.

\clearpage
%=========================================================